\documentclass[../main.tex]{subfiles}

\begin{document}

\paragraph{Slivermoon Guild Campaign S (2020 - ):}
The ongoing Dungeons and Dragons campaign I run for my younger brother and my highschool friends back in Washington state. (On long-term hiatus, close to finishing)
\paragraph{Violet Lotus Campaign V (2022 - ):}
The ongoing Dungeons and Dragons campaign I run for my friends at UC Davis.
\paragraph{Kori no Azuma Campaign K (2021 - ):}
The ongoing Dungeons and Dragons campaign my young brother runs for his friends and I. It takes place in the same universe as my campaigns, but on a different continent.
\paragraph{Serova Founding Calendar:}
The primary date system I use to track the timeline of events taking place in our Dungeons and Dragons universe.
\begin{itemize}
    \item Year 0 marks the founding of the Serova city-state.
    \item The Great Dragon War happened in the year 8866. Rosinya, Gale, and the Asakhan Empire are founded within the proceeding centuries.
    \item The Slivermoon Guild campaign occurs in the years 9373 - 9376.
    \item The Violet Lotus campaign starts in the year 9396.
    \item The date of the Kori no Azuma campaign is to be determined.
\end{itemize}
\paragraph{The Apocalypse Calendar:}
An alternative date system for our Dungeons and Dragons universe. Measures years since the Great Dragon War, encompassing a more human dominated era.
\begin{itemize}
    \item Year 0 marked by the Great Dragon War. Rosinya, Gale, and the Asakhan Empire are founded within the proceeding centuries.
    \item The Slivermoon Guild campaign occurs in the years 507 – 510.
    \item The Violet Lotus campaign occurs in the years 530.
    \item The date of the Kori no Azuma campaign is to be determined.
\end{itemize}
\paragraph{Vilterra:}
The continent that serves as the setting for both the Slivermoon Guild and Violet Lotus campaigns. It encompasses the Asakhan Empire, Rosinya proper, Gale, and the Dwarven Kingdoms, along with the formerly existing Serovean and Meneketes Empires.
\paragraph{Lukanos:}
The all father, the supreme monkee, mr. green man. Lukanos is the ruler of the gods and the universe. Lukanos is the life source of the indominable human spirit to fight Samu’El of all evil. Also happens to hold power of life domain.
\begin{itemize}
    \item Named Followers: xX\_SilentBlade\_Xx\textsubscript{K} (also Monkee)
\end{itemize}
\paragraph{Palid:}
The god of storm, god of lawfulness, and guardian of the afterlife. Palid holds power over the tempest domain. Worshippers of Palid diverge radically on how their interpretations of his belief system, however, are united by their hatred of necromancy and the undead.
\begin{itemize}
    \item Named Followers: Saitama\textsubscript{S}, Zarthos\textsubscript{K}
\end{itemize}
\paragraph{Hestiam:}
The god of familial bonds, individuality, and the hearth fire. Hestiam holds power over the light domain.
\begin{itemize}
    \item Named Followers: Zorzhoon\textsubscript{V}
\end{itemize}
\paragraph{Elon: }
The god of money, scamming, and economic exploitation. Literally the Ferengi from Star Trek. Elon holds power over the trickery domain
\begin{itemize}
    \item Named Followers: Larry Longs\textsubscript{V}
\end{itemize}
\paragraph{Shar:}
The god of Darkness, loss, and necromancy.
\paragraph{Aranakas:}
One of the most powerful Fiend lords; known for taking advantage of people who makes pact with him.
\begin{itemize}
    \item Named Warlock: Fenrir Norns
\end{itemize}
\paragraph{Si’ma*@m’yu\&d’El/Samu’El:}
The physical incarnation of the indifferent cruelty of the universe.
\paragraph{Rosinha/Rosinya:}
A kingdom, located on the central east coast of Vilterra, which serves as the setting for the Violet Lotus campaign. It was founded by Saint Joao Agostino in the decades proceeding the Great Dragon War. This religious origin established the prevalence of Palid worship within the politics, culture, and daily lives of Rosinya’s inhabitants. The kingdom is currently ruled by the Braceo Dynasty and sports an overseas colonial empire. Rosinya has infamously become more tyrannical: dissolving the courts, restoring slavery, increasing surveillance, and persecuting worshippers of Hestiam.
\begin{itemize}
    \item The homeland of: Miguel\textsubscript{V}, Manuel\textsubscript{V}, Andre\textsubscript{V}, Carlos\textsubscript{V}, Francisco\textsubscript{V}, Rodrigo\textsubscript{V}, Alfonso\textsubscript{V}
\end{itemize}
\paragraph{Rosinyean/Rosinhe}
Rosinyean or Rosinhe refers to members of the country’s dominant human ethnic/cultural group. Although these terms can also be applied to non-human inhabitants of Rosinya.
\paragraph{Asakhan Empire:}
The largest contemporary empire on the continent of Vilterra. It is known for its diversity, technical/magical advancements, and strong governmental institutions. However due to the empire’s self-righteousness and militarism, it has attracted the hostility of it’s neighbors. Their longtime rival, Rosinya, has become more aggressive in contesting the Asakhan’s control over Vilterra.
\begin{itemize}
    \item The homeland of: Zorzhoon\textsubscript{V}, Vizmir Mar\textsubscript{SV}, Dain Battlehammer\textsubscript{S}
\end{itemize}
\paragraph{Asakhan:}
A group of humans who originated in the grassland west of Vilterra, and conquered the remnant of Serova to form the Asakhan Empire. Asakhan could also refer to non-human inhabitant or citizens of the Asakhan Empire, particularly high-elves, Tieflings, half-orcs, and half-elves.
\begin{itemize}
    \item Notable Asakhan include: Zorzhoon\textsubscript{V}, Vizmir Mar\textsubscript{S}
\end{itemize}
\paragraph{The Council of One Hundred Kings:}
A loose multi-national organization, this council established laws that all Dwarven kingdoms in the Crown of the World must follow. In practice the council functions similarly to a cartel, regulating the price of precious metals; including gold, silver, tin, and copper.
\begin{itemize}
    \item Volos Ghazant, the king of Thunderpike, is one of its most prominent members.
    \item Larry Longs probably had to navigate the council’s jurisdictions when working as one of Ghazant’s revenue/tax service agents.
\end{itemize}
\paragraph{Thunderpike:}
The largest city-state in the Crown of the World, Thunderpike serves as the de facto center of dwarven civilization. It is historical significant due to the paramount leadership of its ruling dynasty, the Dulmons, during the 9th millennium. Volos Ghazant serves as the currently ruler of Thunderpike.
\begin{itemize}
    \item The homeland of: Larry Longs\textsubscript{V}
\end{itemize}
\paragraph{Gale:}
A kingdom located on the northern east coast of Vilterra. It serves as the setting for the Slivermoon Guild campaign, where the War of the Witch King Occurred.
\begin{itemize}
    \item The homeland of: Shawn Blackcrow\textsubscript{S}, Uruk (Jerry)\textsubscript{S}
\end{itemize}
\paragraph{Frontier:}
A geographic region in the northwest of Vilterra. Known for its desert ecosystem.
\begin{itemize}
    \item The homeland of: Saitama\textsubscript{S}, Aodjkin Leisfeil\textsubscript{V}
\end{itemize}
\paragraph{The Crown of the World:}
A mountain chain on the far north of Vilterra. The traditional homeland of the Dwarves, Dragonborn, and Dragons.
\begin{itemize}
    \item The homeland of: Sum One Else\textsubscript{S}, Larry Longs\textsubscript{V}
\end{itemize}
\paragraph{The Spine of the World:}
The mountain chain along the west end of Vilterra. It is known for it’s Dark Elf and Goliath inhabitances, although there are several Dwarven colonies scattered throughout its peaks.
\paragraph{Serova/Serovean Empire}
A historical regime, which at its greatest extent ruled all of Vilterra. It had a majority High-Elf population and was a ruled by an elected monarchy.
\begin{itemize}
    \item Serovean can refer to people belonging to the Serovean high-elf ethnic/cultural group.
    \item Serova take its name from its capital city of Serova. This metropolis currently serves as the capital of the Asakhan Empire.
\end{itemize}
\paragraph{Meneketes Empire }
A historical regime which served as rivals to the Serovean Empire though the 9th millennium. It was predominantly human and was ruled by the Dragon descent Meneketes Dynasty. The Empire was destroyed during the Great Dragon War, but its lasting impact can still be felt today. The Rosinyean and Galean cultures are descent of the Meneketes, and their language Imperial Mitosi would server the basis of Common,  Modern Rosinyean, and Galean. The Meneketes also introduced the Mitosi alphabet which became the dominant writing system in Vilterra.
\paragraph{The Great Dragon War }
A historical conflict that led to the mutual destruction of both the Serovean and Meneketes empires. It’s name comes from the extensive use of full grown Dragon slaves during the war. This use of dragons would result to the destruction of early major city and mass devastation to Vilterra’s natural ecosystem. This war is the bloodiest conflict in the continent’s history.
\paragraph{Seforean: }
Refers to an inhabitant from the southern continent of Seforea. However colligatively this word is used as a catch all term to describe humans with dark brown skin.

\end{document}
